preciseTAD: A machine learning framework for precise TAD boundary prediction at base pair resolution

### 2020-07-01 Manuscript/manuscript.Rmd
changed title

---
title: Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings
csl: styles.ref/genomebiology.csl
output:
  pdf_document: default
  word_document:
    reference_docx: styles.doc/NIH_grant_style.docx
bibliography: References/references.bib
---

>>>>

---
title: preciseTAD: A machine learning framework for precise TAD boundary prediction at base pair resolution
csl: styles.ref/genomebiology.csl
output:
  word_document:
    reference_docx: styles.doc/NIH_grant_style.docx
  pdf_document: default
bibliography: References/references.bib
---
